Adding selection to \stdpopsim: oh how the tables have turned

### 2024-03-07 analysis2_manuscript.tex
draft of first two paragraphs

% \author[1,+]{M. Elise Lauterbur}
% \author[2,*]{Maria Izabel A. Cavassim}
% \author[3,*]{Ariella L. Gladstein}
% \author[4,*]{Graham Gower}
% \author[5*]{Nathaniel S. Pope}
% \author[6,*]{Georgia Tsambos}
% \author[5,7]{Jeff Adrion}
% \author[5]{Saurabh Belsare}
% \author[8]{Arjun Biddanda}
% \author[5]{Victoria Caudill}
% \author[9]{Jean Cury}
% \author[10]{Ignacio Echevarria}
% \author[11]{Benjamin C. Haller}
% \author[12,13]{Ahmed R. Hasan}
% \author[14,15]{Xin Huang}
% \author[16]{Leonardo Nicola Martin Iasi}
% \author[17]{Ekaterina Noskova}
% \author[18]{Jana Obšteter}
% \author[19]{Vitor Antonio Corrêa Pavinato}
% \author[20,21]{Alice Pearson}
% \author[22,23]{David Peede}
% \author[24]{Manolo F. Perez}
% \author[5]{Murillo F. Rodrigues}
% \author[5]{Chris C. R. Smith}
% \author[25]{Jeffrey P. Spence}
% \author[5]{Anastasia Teterina}
% \author[5]{Silas Tittes}
% \author[26]{Per Unneberg}
% \author[27]{Juan Manuel Vazquez}
% \author[28]{Ryan K. Waples}
% \author[29]{Anthony Wilder Wohns}
% \author[30]{Yan Wong}
% \author[31]{Franz Baumdicker}
% \author[32]{Reed A. Cartwright}
% \author[33]{Gregor Gorjanc}
% \author[34]{Ryan N. Gutenkunst}
% \author[30]{Jerome Kelleher}
% \author[5]{Andrew D. Kern}
% \author[35]{Aaron P. Ragsdale}
% \author[5,36]{Peter L. Ralph}
% \author[37]{Daniel R. Schrider}
% \author[38,+]{Ilan Gronau}

% \affil[*]{\small{These authors contributed equally to the paper.}}

@@

% \affil[4]{\small{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen, Denmark}}
% \affil[5]{\small{Institute of Ecology and Evolution, University of Oregon, Eugene OR 97402, USA}}

@@

\section*{Introduction}
    \label{introduction}

@@

@@

%\bibliography{}
\end{document}

>>>>

% \author[1,+]{M. Elise Lauterbur}
% \author[2,*]{Maria Izabel A. Cavassim}
% \author[3,*]{Ariella L. Gladstein}
 \author[4,*]{Graham Gower}
 \author[5*]{Nathaniel S. Pope}
% \author[6,*]{Georgia Tsambos}
% \author[5,7]{Jeff Adrion}
% \author[5]{Saurabh Belsare}
% \author[8]{Arjun Biddanda}
% \author[5]{Victoria Caudill}
% \author[9]{Jean Cury}
% \author[10]{Ignacio Echevarria}
% \author[11]{Benjamin C. Haller}
% \author[12,13]{Ahmed R. Hasan}
% \author[14,15]{Xin Huang}
% \author[16]{Leonardo Nicola Martin Iasi}
% \author[17]{Ekaterina Noskova}
% \author[18]{Jana Obšteter}
% \author[19]{Vitor Antonio Corrêa Pavinato}
% \author[20,21]{Alice Pearson}
% \author[22,23]{David Peede}
% \author[24]{Manolo F. Perez}
% \author[5]{Murillo F. Rodrigues}
% \author[5]{Chris C. R. Smith}
% \author[25]{Jeffrey P. Spence}
% \author[5]{Anastasia Teterina}
% \author[5]{Silas Tittes}
% \author[26]{Per Unneberg}
% \author[27]{Juan Manuel Vazquez}
% \author[28]{Ryan K. Waples}
% \author[29]{Anthony Wilder Wohns}
% \author[30]{Yan Wong}
% \author[31]{Franz Baumdicker}
% \author[32]{Reed A. Cartwright}
% \author[33]{Gregor Gorjanc}
% \author[34]{Ryan N. Gutenkunst}
% \author[30]{Jerome Kelleher}
% \author[5]{Andrew D. Kern}
% \author[35]{Aaron P. Ragsdale}
% \author[5,36]{Peter L. Ralph}
% \author[37]{Daniel R. Schrider}
% \author[38,+]{Ilan Gronau}

 \affil[*]{\small{These authors contributed equally to the paper.}}

@@

 \affil[4]{\small{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen, Denmark}}
 \affil[5]{\small{Institute of Ecology and Evolution, University of Oregon, Eugene OR 97402, USA}}

@@

\section*{Introduction}
    \label{introduction}
As the complexity of population genetic datasets has increased,
simulation has become a critical tool for interpretation, 
analysis, and exploration of realistic evolutionary models.
Simulation in population genetics has a long history 
including both backward in time coalescent simulations
\citep{kingman1982genealogy,hudson1983testing, hudson1990gene}
and forward in time simulations of complex demography and selection
\citep[e.g.,][]{gillespie1984molecular,thornton2014c++, haller2019slim}.
The development of simulation tools has been driven by the need to
understand the effects of complex evolutionary processes on genetic
variation, to provide a null model for hypothesis testing, to
to explore the power and limitations of statistical methods, and 
increasingly to provide a basis for machine learning and other
simulation-based inference methods.

A lingering challenge with simulation in population genetics has been
reproducibility and the ability to share and compare results among 
researchers. This challenge has been addressed in part by the development
of community resources for sharing and distributing simulation software
via the \stdpopsim project \citep{adrion2020community}. \stdpopsim
provides a standardized interface for accessing a wide range of
population genetic models, and has begun to be be widely adopted by the community.
While that is so, the current version of \stdpopsim does not include
models of selection, which is a major limitation for many applications
of population genetic simulation. In particular, modeling selection
through simulation is critical for understanding the processes such
as adaptation, the effects of selective sweeps, and the impact of
background selection on genetic diversity. Ideally, one would like
to have a single, unified framework for simulating both neutral and
non-neutral evolutionary processes, and to be able to compare the
results of these simulations to empirical data in a manner that is
accessible to a wide range of researchers and highly reproducible. 
Further the framework should include the complex realities of 
genomes, including heterogenous recombination rates, 
variation in the density of functional elements, and relevant
population size histories.

@@

    \begin{figure}[ht]
        \centering
        \includegraphics[width=\textwidth]{figures/HomSap/estimated_Ne_t_final}
        \caption{
        \label{fig:demography}
        Performance of methods to infer human OOA model
        with and without background selection on exons.
        }
    \end{figure}

    \begin{figure}[ht]
        \centering
        \includegraphics[width=\textwidth]{figures/HomSap/dfe.inference.benchmark}
        \caption{
        \label{fig:dfe_humans}
        Performance of methods to infer distribution of fitness effects (DFE).
        }
    \end{figure}

    \begin{figure}[ht]
        \centering
        \includegraphics[width=\textwidth]{figures/PhoSin/dfe.inference.benchmark}
        \caption{
        \label{fig:dfe_vaquita}
        Performance of methods to infer distribution of fitness effects (DFE).
        }
    \end{figure}

@@

\bibliography{references.bib}
\end{document}
